---
title: "Final Project"
author: 
 - Dahye Chung, Donguk Yoo, Hanseung Jang, Sanghyun Lee, Jungyoon Choi, 
 - Seokyeong Park, Semin Seo, Boyeon Kim
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
    extra_dependencies: ["kotex"]
    keep_tex: true
     
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
ditor_options:
  chunk_output_type: console
---

```{r, warning = FALSE, message= FALSE}
library(tidyverse)
library(broom)
library(tidyr)
library(dplyr)
library(modelr)
library(boot)
library(tidyr)
library(ggplot2)
library(ggmosaic)
library(dplyr)
library(readr)
library(class)
library(caret)
library(infer)
```

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Cost function for cross validation
cost <- function(obs, pred) {
  outcome <- pred > 0.5
  return(1 - (sum(obs == outcome) / length(obs)))
}
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggmosaic))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(boot))
```

#Intro
```{r, message=FALSE}
library(tidyr)
library(ggplot2)
library(ggmosaic)
library(dplyr)
Sleep_health_and_lifestyle_dataset <- read_csv("Sleep_health_and_lifestyle_dataset.csv")
```

```{r}
Sleep_health_and_lifestyle_dataset_renamed <- Sleep_health_and_lifestyle_dataset %>%
  rename( Duration = 'Sleep Duration',
          Stress = 'Stress Level',
          Physical = 'Physical Activity Level' ,
          Quality = 'Quality of Sleep' ,
          BMI= 'BMI Category' ,
          BPressure = 'Blood Pressure' ,
          HRate = 'Heart Rate' ,
          DSteps = 'Daily Steps' ,
          Disorder = 'Sleep Disorder' )
```

#Hypothesis Testing

```{r}
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Overweight"] <- "High"
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Obese"] <- "High"
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Normal Weight"] <- "Normal"
```

```{r, message=FALSE}
Sleep_health_and_lifestyle_dataset_renamed %>%
  filter(BMI == "Normal" | BMI == "High") %>%
  ggplot() +
  geom_histogram( 
    mapping = aes(x = Duration, fill = BMI), 
    position = "identity",
alpha = 0.5
  )
```



```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  filter(BMI == "Normal" | BMI == "High") %>%
  ggplot() +
  geom_density( 
    mapping = aes(x = Duration, fill = BMI), 
    position = "identity",
alpha = 0.5
  )
```


```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
summarize(
mean = mean(Duration),
median = median(Duration), 
standard_deviation = sd(Duration), 
minimum = min(Duration),
maximum = max(Duration)
)
```




```{r}
Model <- lm(Duration ~ BMI, data = Sleep_health_and_lifestyle_dataset_renamed)
Simulation_results <-
  Sleep_health_and_lifestyle_dataset_renamed %>%
  specify(Duration ~ BMI) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("Normal", "High"))
```


```{r}
Shl_obs_stat <-
  Sleep_health_and_lifestyle_dataset_renamed %>%
  specify(formula = Duration ~ BMI) %>%
  calculate(stat = "diff in means", order = c("Normal","High"))
```

```{r}
Shl_null <- Sleep_health_and_lifestyle_dataset_renamed %>%
  specify(Duration ~ BMI) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute")
```

```{r}
Shl_null %>% get_p_value(obs_stat = Shl_obs_stat, direction = "right")

```

```{r}
p_value <- Shl_null %>% get_p_value(obs_stat = Shl_obs_stat, direction = "right")
```


```{r}
Simulation_results %>%
 visualize() +
 shade_p_value(obs_stat = Shl_obs_stat, direction = "right")
```


#Predictive Analysis

###Load the dataset

```{r, warning = FALSE, message= FALSE}

Sleep_health_and_lifestyle_dataset <- read_csv(file = "Sleep_health_and_lifestyle_dataset.csv",
  col_types = cols(
    'Person ID' = col_character(),
    'Age' = col_double(),
    'Sleep Duration' = col_double(),
    'Stress Level' = col_double(),
    'Physical Activity Level' = col_double(),
    'Quality of Sleep' = col_double(),
    'BMI Category' = col_character(),
    'Blood Pressure' = col_character(),
    'Heart Rate' = col_double(),
    'Daily Steps' = col_double(),
    'Sleep Disorder' = col_character()
  ))

```

###Rename

```{r, warning = FALSE, message= FALSE}

Sleep_health_and_lifestyle_dataset_renamed <- Sleep_health_and_lifestyle_dataset %>%
  rename(ID = 'Person ID',
         Duration = 'Sleep Duration',
         Stress = 'Stress Level',
         Physical = 'Physical Activity Level',
         Quality = 'Quality of Sleep',
         BMI = 'BMI Category',
         BPressure = 'Blood Pressure',
         HRate = 'Heart Rate',
         DSteps = 'Daily Steps',
         Disorder = 'Sleep Disorder')
```
###Parse Sleep Data
```{r, warning = FALSE, message= FALSE}

sleep_data <- Sleep_health_and_lifestyle_dataset_renamed %>%
    mutate(sufficient_sleep = as.logical(Duration >= 7.0))
```

###Sleep Data Disorders
```{r, warning = FALSE, message= FALSE}
sleep_data %>%
  pivot_longer(cols = c(Disorder), names_to = "variable", values_to = "value") %>%
  group_by(variable, value, sufficient_sleep) %>%
  summarise(count = n()) %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = value, y = count, fill = sufficient_sleep),
    position = "dodge",   
    alpha = 0.6,
    stat = "identity"
  ) +
  facet_wrap(~ variable, scales = "free") +
  labs(title = "Distribution of Sufficient Sleep across Disorders",
       x = "Disorder Type", 
       y = "Count", 
       fill = "Sufficient Sleep")
```

###Sleep Data Gender

```{r, warning = FALSE, message= FALSE}
sleep_data %>%
  pivot_longer(cols = c(Gender), names_to = "variable", values_to = "value") %>%
  group_by(variable, value, sufficient_sleep) %>%
  summarise(count = n()) %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = value, y = count, fill = sufficient_sleep),
    position = "dodge",  
    alpha = 0.6,
    stat = "identity"
  ) +
  facet_wrap(~ variable, scales = "free") +
  labs(title = "Distribution of Sufficient Sleep by Gender",
       x = "Value", 
       y = "Count", 
       fill = "Sufficient Sleep")

```

###Sleep Data BMI

```{r, warning = FALSE, message= FALSE}
sleep_data %>%
  pivot_longer(cols = c(BMI), names_to = "variable", values_to = "value") %>%
  mutate(value = ifelse(value == "Normal", "Normal Weight", value)) %>%
  group_by(variable, value, sufficient_sleep) %>%
  summarise(count = n()) %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = value, y = count, fill = sufficient_sleep),
    position = "dodge",   
    alpha = 0.6,
    stat = "identity"
  ) +
  facet_wrap(~ variable, scales = "free") +
  labs(title = "Distribution of Sufficient Sleep by BMI Category",
       x = "Value", 
       y = "Count", 
       fill = "Sufficient Sleep")

```

###Mode

```{r, warning = FALSE, message= FALSE}
mode_gender <- as.character(names(which.max(table(sleep_data$Gender))))
mode_occupation <- as.character(names(which.max(table(sleep_data$Occupation))))
mode_bmi <- as.character(names(which.max(table(sleep_data$BMI))))

sleep_data <- sleep_data %>%
mutate(
  Gender = if_else(is.na(Gender), mode_gender, Gender),
  Occupation = if_else(is.na(Occupation), mode_occupation, Occupation),
  BMI = if_else(is.na(BMI), mode_bmi, BMI)
)

```

###Sufficient Sleep

```{r, warning = FALSE, message= FALSE}
sleep_data$sufficient_sleep <- ifelse(sleep_data$Duration >= 7, "Sufficient", "Insufficient")

```

###Saparate Train, Test Set

```{r, warning = FALSE, message= FALSE}
set.seed(123)
train_indices <- createDataPartition(sleep_data$sufficient_sleep, p = 0.7, list = FALSE)
trainingSet <- sleep_data[train_indices, ]
testSet <- sleep_data[-train_indices, ]

trainingSet$sufficient_sleep <- as.factor(trainingSet$sufficient_sleep)
testSet$sufficient_sleep <- as.factor(testSet$sufficient_sleep)

training_Outcomes <- trainingSet$sufficient_sleep
test_Outcomes <- testSet$sufficient_sleep
```

###Train
```{r, warning = FALSE, message= FALSE}
model <- glm(sufficient_sleep ~ Age + Gender + Occupation + Physical + DSteps + BMI, data = trainingSet, family = binomial)
```

###Predict
```{r, warning = FALSE, message= FALSE}
predictions <- predict(model, newdata = testSet, type = "response")
```

###Test
```{r, warning = FALSE, }

threshold <- 0.5  
predicted_classes <- as.factor(ifelse(predictions >= threshold, "Sufficient", "Insufficient"))
actual_classes <- test_Outcomes
accuracy <- sum(predicted_classes == actual_classes) / length(actual_classes)
print(paste("Accuracy:", accuracy))

model_1_preds <- testSet %>%
  add_predictions(model, type = "response") %>%
  mutate(
    outcome = as.factor(if_else(condition = pred > threshold, 
                      "Sufficient", "Insufficient"))
  )

```

# Data Visualization
```{r}
Sleep_health_and_lifestyle_dataset_renamed <- Sleep_health_and_lifestyle_dataset%>%
  rename( ID = "Person ID",
          Duration = 'Sleep Duration',
          Stress = 'Stress Level',
          Physical = 'Physical Activity Level' ,
          Quality = 'Quality of Sleep' ,
          BMI= 'BMI Category' ,
          BPressure = 'Blood Pressure' ,
          HRate = 'Heart Rate' ,
          DSteps = 'Daily Steps' ,
          Disorder = 'Sleep Disorder' )
```

```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot()+
  geom_point( mapping = aes( x = Age , y = Duration, color = Gender))+
  labs(
   title = "Sleep Duration vs Age (by gender)",
   x= "Age", y = " Duration")
```

```{r}
model_2 <- lm(Duration ~ Physical,Sleep_health_and_lifestyle_dataset_renamed)
```

```{r}
model_2$coefficients
```
```{r, warning=FALSE}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
  geom_point(mapping = aes(x = Physical, y = Duration), bin = 10) +
  geom_abline(slope = model_2$coefficients[2], 
              intercept = model_2$coefficients[1])+
   labs(x = "Physical Activity Level", y = "Sleep Duration",
                    title = "physical activity level vs sleep duration" )
```
# Data Wrangling
```{r}
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Overweight"] <- "Fat"
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Obese"] <- "Fat"
Sleep_health_and_lifestyle_dataset_renamed$BMI[Sleep_health_and_lifestyle_dataset_renamed$BMI == "Normal Weight"] <- "Normal"
```


```{r}
head(Sleep_health_and_lifestyle_dataset_renamed) %>%
  select(ID, HRate, Duration, Gender, Age, Occupation, Physical, BMI, Quality) %>%
  arrange(Duration)
```


```{r}
tail(Sleep_health_and_lifestyle_dataset_renamed) %>%
 select(ID, HRate, Duration, Gender, Age, Occupation, Physical, BMI, Quality) %>%
  arrange(Duration) %>%
  filter(Gender == 'Female')
```


```{r}
head(Sleep_health_and_lifestyle_dataset_renamed) %>%
 select(ID, HRate, Duration, Gender, Age, Occupation, Physical, BMI, Quality) %>%
  arrange(Duration) %>%
  filter(Gender == 'Male')
```

# EDA

###Explore dataset

```{r}
head(Sleep_health_and_lifestyle_dataset)
```
```{r}
tail(Sleep_health_and_lifestyle_dataset)
```

```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  summarize(
    standard_deviation = sd(HRate)
    
  )
```
# Visualizing data
###Histogram
```{r, message=FALSE}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_histogram(mapping = aes(x = HRate), color = "pink", fill = "lightgreen") +
    labs(title = "Count of Heart Rate", x = "Heart rate") 
```

###Box plot

```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_boxplot(mapping = aes(x = HRate)) +
    labs(title = "Boxplot of Individual Heart Rate", x = "Heart rate")
```
### Violin plot
```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_violin(mapping = aes(x = HRate, y ="")) +
    labs(title = "Violin of Individual Heart rate", x = "Heart rate", y = "y")
```

###Bar Graph
```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_bar(mapping = aes(x = BMI), color = "black", fill = "yellow") +
    labs(title = "BMI Count", x = "BMI")
```

###Box plot
```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_boxplot(mapping = aes(x = BMI, y = Duration)) +
    labs(title = "Relationship between BMI and Duration", x = "BMI")
```
###Violin plot
```{r}
Sleep_health_and_lifestyle_dataset_renamed %>%
  ggplot() +
    geom_violin(mapping = aes(x = BMI, y = Duration)) +
    labs(title = "Relationship between BMI and Duration", x = "bmi", y = "Duration")
```

###Scatter plot_Duration and Heart Rate

```{r}
Sleep_health_and_lifestyle_dataset_renamed    %>% 
ggplot()    +
geom_point(mapping = aes(x = BMI, y = Duration))    + 
labs(
title = "Scatter plot of Duration and Heart Rate", 
x = "BMI",
y = "Duration" 
)
```


# Modeling 


```{r}
Sleep_health_and_lifestyle_dataset_renamed%>%
  ggplot()+
  geom_point( mapping = aes( x  = Physical , y = Duration)) +
  labs(title = "Relationships between Physical activies and Duration",
       x = "Physical Activities" , y = "Duration")
```






```{r}

data <- Sleep_health_and_lifestyle_dataset_renamed

model <- lm(Duration ~ Physical, data = Sleep_health_and_lifestyle_dataset_renamed)


summary(model)

```

```{r, message=FALSE}
residuals <- residuals(model)

qqnorm(residuals)
qqline(residuals)
labs( title  = "QQplot" , x = "Theoretical" , y = "Quantaties")
```

```{r}
Renamed_other_model <- lm(Duration ~ Physical, data = Sleep_health_and_lifestyle_dataset_renamed)

```

```{r}
Renamed_other_model$coefficients
```

```{r}
Renamed_other_model%>%
  tidy()
```

```{r}
Renamed_other_model%>%
  glance()%>%
  select(r.squared)
```

```{r}
Sleep_health_and_lifestyle_dataset_renamed%>%
  ggplot()+
  geom_point(mapping = aes( x  = Physical , y = Duration) )+
  geom_abline(slope = Renamed_other_model$coefficients[2]	,
              intercept = Renamed_other_model$coefficients[1]  )+
  labs( title = "Relationships between Physical and Duration",
        x = " Physical ",
        y = " Duration" )

```

#Advanced Modeling 


```{r}
continuous_model <- lm(Duration ~ Gender + Age + Occupation + DSteps + BMI + Physical, data = Sleep_health_and_lifestyle_dataset_renamed)
coefficients <- tidy (continuous_model)
coefficients
```

```{r}
r_squared <- glance(continuous_model)$r.squared
```

```{r}
Sleep_health_and_lifestyle_dataset_df <- Sleep_health_and_lifestyle_dataset_renamed %>%
  add_predictions(continuous_model) %>%
  add_residuals(continuous_model)
```

###Histogram of residual in Sleep_health_and_lifestyle_dataset_df
```{r}
Sleep_health_and_lifestyle_dataset_df %>%
  ggplot() +
  geom_histogram(mapping = aes(x = resid), color = "blue", fill = "pink", bins = 10) +
  labs(x = "residual", y ="Duration",
title = "Histogram of residual in Sleep_health_and_lifestyle_dataset_df")
```

###Observed vs. Predicted Plot
```{r}
Sleep_health_and_lifestyle_dataset_df %>%
  ggplot() +
  geom_point(mapping = aes(x = pred, y = Duration)) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Observed vs. Predicted Plot", x = "Predicted Duration", y = "Observed Duration")
```

###Residual vs Predicted Plot
```{r}
Sleep_health_and_lifestyle_dataset_df %>%
  ggplot() +
  geom_point(mapping = aes(x = pred, y = resid)) +
  geom_hline(yintercept = 0) +
  labs( title= "Residual vs Predicted Plot",
        x = "Predicted Duration",
        y = "Residuals")
```

###Q-Q Plot (Obeserved vs Predicted Plot)
```{r, message=FALSE}
Sleep_health_and_lifestyle_dataset_df %>%
  ggplot() +
  geom_qq(aes(sample = resid)) +
  geom_qq_line(aes(sample = resid))+
  labs(title = "Q-Q plot of residuals", x= "Predicted Duration", y= "Observed Duration")
```

###Box Plot
```{r, fig.width=15}
Sleep_health_and_lifestyle_dataset_df %>%
  pivot_longer(
    cols = Gender:Occupation | Physical | BMI | DSteps,
    names_to = "column",
    values_to = "value",
    values_transform = list(value = 'factor')
) %>%
ggplot() +
  geom_boxplot(aes(x = reorder(value, Duration, FUN = median), y = Duration)) +
  facet_wrap(~column, scales = "free_x") +
  labs(x = "x variable", y = "Duration", title = "Box Plot of x variables") +
  theme(axis.text.x = element_text(angle = 45))
```






